Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-15 paper.tex
typo

Our implementation guidelines emphasize on writing short and readable code,
easily maintainable by external contributors, while being as efficient as
possible.  Whenever practicable, algorithms implemented in \sklearn are thus
directly written in pure Python. For intensive numerical computations, the
library mostly relies on NumPy vector operations, which allows for the code to
remain concise and readable while being efficient. For all algorithms that
cannot be easily and efficiently expressed as NumPy operations, we rely on
Cython \citep{behnel2011cython}  for writing the critical parts and achieving
decent performance and scalability. Cython is a compiled programming language
that extends Python with static typing. It produces efficient C extension
modules that are directly importable from the Python runtime system. Examples of
algorithms written in Cython include stochastic gradient descent for linear
models, some graph-based clustering algorithms or decision trees. To facilitate
the adoption of the library, we also limit to a bare minimum the set of external
depencies. As such, NumPy and SciPy -- the two most common dependencies in the
Python scientific ecosystem -- are actually the only two required dependencies
for the library to fully work. Some modules may rely on other external
libraries, but then we tend to prefer to directly ship them within the codebase
rather than adding new dependencies. In particular, the codebase ships modified
versions of the \textsf{LIBSVM} and \textsf{LIBLINEAR} libraries
\citep{chang2011libsvm,fan2008}, both written in C{}\verb!++! and wrapped using
Cython modules.

@@

To ease code reuse, object-oriented techniques and design patterns are used all
throughout the codebase. In particular, the \textit{duck typing} design pattern
is widely exploited to simplify implementation and skip the introduction of
superfluous classes. This technique indeed allows both for extensibility and
flexibility: user-defined estimators that follow our API and conventions should
be reusable (e.g., in a pipeline) as any built-in estimators, without them
actually inheriting from our base classes.

>>>>

Our implementation guidelines emphasize on writing short and readable code,
easily maintainable by external contributors, while being as efficient as
possible.  Whenever practicable, algorithms implemented in \sklearn are thus
directly written in pure Python. For intensive numerical computations, the
library mostly relies on NumPy vector operations, which allows for the code to
remain concise and readable while being efficient. For all algorithms that
cannot be easily and efficiently expressed as NumPy operations, we rely on
Cython \citep{behnel2011cython}  for writing the critical parts and achieving
decent performance and scalability. Cython is a compiled programming language
that extends Python with static typing. It produces efficient C extension
modules that are directly importable from the Python runtime system. Examples of
algorithms written in Cython include stochastic gradient descent for linear
models, some graph-based clustering algorithms or decision trees. To facilitate
the adoption of the library, we also limit to a bare minimum the set of external
dependencies. As such, NumPy and SciPy -- the two most common dependencies in the
Python scientific ecosystem -- are actually the only two required dependencies
for the library to fully work. Some modules may rely on other external
libraries, but then we tend to prefer to directly ship them within the codebase
rather than adding new dependencies. In particular, the codebase ships modified
versions of the \textsf{LIBSVM} and \textsf{LIBLINEAR} libraries
\citep{chang2011libsvm,fan2008}, both written in C{}\verb!++! and wrapped using
Cython modules.

@@

To ease code reuse, object-oriented techniques and design patterns are also used
all throughout the codebase. In particular, the \textit{duck typing} design
pattern is widely exploited to simplify implementation and skip the introduction
of superfluous classes. This technique indeed allows both for extensibility and
flexibility: user-defined estimators that follow our API and conventions should
be reusable (e.g., in a pipeline) as any built-in estimators, without them
actually inheriting from our base classes.
